---
title: "Age Expanded Malaria Community Case Management in Malawi"
author: "TRUE/CDC OR Working Group"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_collapse: no
    toc_depth: 3
    toc_float: yes
    css: C:/Users/omp2/OneDrive - CDC/Cambodia_03_25_19/analysis/cambodia_g6pd/style.css

---


<div class="watermark">PRELIMINARY</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      fig.width = 7,
                      fig.height = 6,
                      dpi = 500,
                      warning = FALSE,
                      message = FALSE)
```



# Import {.tabset .tabset-fade}
## Packages
```{r class.source = 'fold-show'}
if (!require(pacman)) {
      install.packages("pacman", dependencies = TRUE)
}

pacman::p_load_gh("deansayre/Rtesunate", "reconhub/linelist") # loads packages downloaded from GitHub

pacman::p_load(DT,                                            # loads packages downloaded from CRAN
               rio, 
               flextable,
               conflicted,
               tidyverse)

conflict_prefer("filter", "dplyr")                            # creates preference for filter function from dplyr
```


## Functions
Currently transitioning to package Rtensunate for functions. 
```{r eval=F}
# Separate R file with custom functions
source("functions.R")

```

## Data

```{r class.source = 'fold-show'}

mccm_redcap <- rio::import("data/data_052222.csv")   # data downloaded from RedCap on 05.22.22

mccm_true <- import("data/true_cleaned_neno_salima_20220425.dta") %>% 
  linelist::clean_data(guess_dates = F)

for (var in colnames(mccm_true)) {
  attr(mccm_true[[deparse(as.name(var))]], "label") <- NULL    #removes label attribute from stata
  attr(mccm_true[[deparse(as.name(var))]], "format.stata") <- NULL
}


dict_redcap <- import("data/dictionary.xlsx")
q_redcap <- import("data/questions1.xlsx")
  

# see "dictionary.R" for information on how dictionary created 

```


## Raw Data used
Will only be filled in when output encoded for partners
```{r eval = F}

mccm_prelim %>% datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('pdf', 'excel'),
                          lengthMenu  = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


# Cleaning {.tabset}
## Comparing Cleaned data and data from RedCap
### Available Variables

```{r }
mccm_full <- mccm_redcap %>% 
  linelist::clean_data(guess_dates = F) %>% 
  arrange(sdi_householdid, redcap_repeat_instance)   # forces order by household, then individual
 # fill(sdi_interview_date, .direction = "up")   # fills variables for individuals collected at household level

mccm_red_house <- mccm_full %>% 
  filter(is.na(redcap_repeat_instance)) %>%         # keeps only those without an individual id entry i.e. households
  squeaky_clean() %>% 
  mutate(district = factor(word(sdi_householdid, 1, sep = "_")),
         hf = factor(word(sdi_householdid, 2, sep = "_")), 
         catchment = factor(word(sdi_householdid, 3, sep = "_")), 
         household = factor(word(sdi_householdid, 4, sep = "_")))




indiv_num <- c("hdi_b03_month",                 #vector of columns that should remain numeric
               "hdi_b03_year", 
               "hmi_arrival_time", 
               "hmi_wait_time", 
               "hmi_sick_duration", 
               "hmi_off_dur", 
               "hmi_pay_care", 
               "hmi_amount_consult", 
               "hmi_amount_rdt", 
               "hmi_amount_trans", 
               "hmi_total_pay", 
               "md_med_duration", 
               "diar_days_aftertreat", 
               "diar_med_amount", 
               "diar_consult_amount",
               "diar_trans_amount", 
               "diar_total_pay")

  
  
  


mccm_red_indiv <- mccm_full %>% 
  filter(!is.na(redcap_repeat_instance)) %>%             # keeps only those with an individual id entry
  squeaky_clean() %>%    #converts numeric classes to factors except those noted
  mutate(unique_id = paste0(sdi_householdid, ".", redcap_repeat_instance), 
         age_yr = ifelse(hdi_b03_age == 0, hdi_b03_month/12, 
                         ifelse(hdi_b03_age == 1, hdi_b03_year, NA_real_)), 
         district = factor(word(sdi_householdid, 1, sep = "_")), 
         hf = factor(word(sdi_householdid, 2, sep = "_")), 
         catchment = factor(word(sdi_householdid, 3, sep = "_")), 
         household = factor(word(sdi_householdid, 4, sep = "_"))) %>% 
  relocate(unique_id)



## Cleaned data set received by email #########################################

a <- setdiff(names(mccm_true), names(mccm_full))
a_df <- q_redcap %>% 
  filter(`Variable / Field Name` %in% a) %>% 
  flextable()

b <- setdiff(names(mccm_full), names(mccm_true))
b_df <- q_redcap %>% 
  filter(`Variable / Field Name` %in% b)%>% 
  flextable()

c <- setdiff(unique(q_redcap$`Variable / Field Name`), names(mccm_full))
c_df <- q_redcap %>% 
  filter(`Variable / Field Name` %in% c)%>% 
  flextable()

d <- setdiff(unique(q_redcap$`Variable / Field Name`), names(mccm_true))
d_df <- q_redcap %>% 
  filter(`Variable / Field Name` %in% d)%>% 
  flextable()

e <- setdiff(names(mccm_true), unique(q_redcap$`Variable / Field Name`))
```

Variables in the cleaned dataset shared by email, but not in RedCap database:
`r a_df`. 

Variables in the RedCap database but not in the database shared by email:
`r b_df`

Variables in the defined in the dictionary, but not in the RedCap database:
`r c_df`

Variables in the defined in the dictionary, but not in the mailed database:
`r d_df`

**NOTE** Many of these are 'select all that apply' variables, which appear because
of the way they are coded in the database with an appended number. These 
variables are unlikely to be truly missing.

### Observations

```{r}
mccm_true_house <- mccm_true %>% 
  filter(is.na(individual_id)) %>%         # keeps only those without an individual id entry i.e. households
  squeaky_clean() %>% 
  mutate(district = factor(word(sdi_householdid, 1, sep = "_")),
         hf = factor(word(sdi_householdid, 2, sep = "_")), 
         catchment = factor(word(sdi_householdid, 3, sep = "_")), 
         household = factor(word(sdi_householdid, 4, sep = "_")))




indiv_num <- c("hdi_b03_month",                 #vector of columns that should remain numeric
               "hdi_b03_year", 
               "hmi_arrival_time", 
               "hmi_wait_time", 
               "hmi_sick_duration", 
               "hmi_off_dur", 
               "hmi_pay_care", 
               "hmi_amount_consult", 
               "hmi_amount_rdt", 
               "hmi_amount_trans", 
               "hmi_total_pay", 
               "md_med_duration", 
               "diar_days_aftertreat", 
               "diar_med_amount", 
               "diar_consult_amount",
               "diar_trans_amount", 
               "diar_total_pay")

  
  
  


mccm_true_indiv <- mccm_true %>% 
  filter(!is.na(individual_id)) %>%             # keeps only those with an individual id entry
  squeaky_clean() %>%    #converts numeric classes to factors except those noted
  mutate(unique_id = paste0(sdi_householdid, ".", individual_id), 
         #age_yr = ifelse(hdi_b03_age == 0, hdi_b03_month/12,                 column doesn't exist in this set
         #               ifelse(hdi_b03_age == 1, hdi_b03_year, NA_real_)),   column doesn't exist in this set
         district = factor(word(sdi_householdid, 1, sep = "_")), 
         hf = factor(word(sdi_householdid, 2, sep = "_")), 
         catchment = factor(word(sdi_householdid, 3, sep = "_")), 
         household = factor(word(sdi_householdid, 4, sep = "_"))) %>% 
  relocate(unique_id)

a <- arsenal::comparedf(mccm_true_indiv, mccm_red_indiv)

a_df <- a[["vars.summary"]] %>% 
  slice(-c(165:173)) %>% 
  mutate(rows = map_int(values, nrow)) %>% 
  filter(rows > 0)


a_display <- a_df %>% 
  select(Variable = var.x, 
         `Number Observations Changed` = rows) %>% 
  flextable()

b <- arsenal::comparedf(mccm_true_house, mccm_red_house)

b_df <- b[["vars.summary"]] %>% 
  slice(-c(140:145)) %>% 
  mutate(rows = map_int(values, nrow)) %>% 
  filter(rows > 0)

b_display <- b_df %>% 
  select(Variable = var.x, 
         `Number Observations Changed` = rows) %>% 
  flextable()


a_display

b_display
```
Listed above the comparisons of the observations in each data set and how 
many observations were changed between the RedCap data set (downloaded on 05.22.22)
and the clean dataset shared via email. More information for each variable is 
availabe in R by examining the nested dataframe, which explicitly states which
observations are different and how. 

```{r eval = F}
### section in progress

## finding selection multiple options



# provides variables in individual database that AREN'T in options/data dictionary. # Some variables that are no multiple choice questions aren't lised in data dictionary, but this also gives the ones that have numbers appended to the end (which is how multi-selects are handled)

a <- setdiff(names(mccm_indiv), unique(options$`Variable / Field Name`)) %>%   
  as.data.frame() %>% 
  rename(variable = 1) %>% 
  filter(str_detect(variable, "_\\d+$")) %>%     # only those that end with a digit after an underscore
  mutate(variable1 = word(variable , 1  , -2, sep = "_"))  # removes last "word" in string (the terminal digit)
  
b <- unique(a$variable1)  ## list of likely candidates for select mulitple option questions

temp_dict <- options %>% 
  dplyr::filter(`Variable / Field Name` %in% b) %>% 
  linelist::clean_data(guess_dates = F) %>% 
  mutate(variable1 = paste0(variable_field_name, "_", att), 
         variable2 = paste0(variable_field_name, "_", value)) %>% 
  select(variable1, variable2) %>% 
  relocate(variable2) %>% 
  tibble::deframe()

temp_dict1 <- options %>% 
  dplyr::filter(`Variable / Field Name` %in% b) %>% 
  linelist::clean_data(guess_dates = F) %>% 
  mutate(new_var = paste0(variable_field_name, "_", value)) %>% 
  select(new_var) %>% 
  #relocate(variable2) %>% 
  tibble::deframe()

c <- setdiff(temp_dict, names(mccm_indiv))
d <- setdiff(temp_dict1, names(mccm_indiv))

temp_dict2 <- temp_dict[!temp_dict %in% c]
temp_dict3 <- temp_dict1[!temp_dict1 %in% c]

indiv <- mccm_indiv %>% 
  dplyr::rename(!!temp_dict2) %>% 
  janitor::clean_names() %>% 
  mutate(across(all_of(temp_dict2), ~factor(.)))

names(indiv)

multfreqtable = function(data, question.prefix) {
  z = length(question.prefix)
  temp = vector("list", z)

  for (i in 1:z) {
    a = grep(question.prefix[i], names(data))
    b = sum(data[, a] != 0, na.rm = T)
    d = colSums(data[, a] != 0, na.rm = T)
    e = sum(rowSums(data[,a], na.rm = T) !=0, na.rm = T)
    f = as.numeric(c(d, b))
    temp[[i]] = data.frame(question = c(sub(question.prefix[i], 
                                            "", names(d)), "Total"),
                           freq = f,
                           percent_response = (f/b)*100,
                           percent_cases = (f/e)*100 )
    names(temp)[i] = question.prefix[i]
  }
  temp
}

multfreqtable(mccm_indiv, "hmi_sect_seek_cure", yes = 1, no = 0)


a <- names(mccm_indiv)[str_detect(names(mccm_indiv), "hmi_sect_seek_cure")]
z <- length(a)
temp <- vector("list", z)



dt <- mccm_indiv %>% 
  select(starts_with("hmi_sect_seek_cure")) %>% 
  mutate(across(.cols = everything(), ~as.numeric(as.character(.)))) %>% 
  mutate(present = rowSums(across(where(is.numeric)), na.rm = T))  # gives total column, if na there are no data for this column

denominator <- sum(!is.na(dt$present))    # number of observations with at least some data entered
denom1 <- sum(dt$present, na.rm = T)

dt1 <- mccm_indiv %>% 
  select(starts_with("hmi_sect_seek_cure")) %>% 
  mutate(across(.cols = everything(), ~as.numeric(as.character(.))))
tots <- colSums(dt1, na.rm = T)
tots_n <- names(tots)
tots_fin <- bind_cols(tots_n, tots) %>% 
  rename(var = 1, 
         n = 2) %>% 
  mutate(perc = round(100*n/denominator,2), 
         perc1 = round(100*n/denom1,2))




```

# Inspection

```{r}

```

