---
title: "Age Expanded Malaria Community Case Management in Malawi"
author: "TRUE/CDC OR Working Group"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_collapse: no
    toc_depth: 3
    toc_float: yes
    css: C:/Users/omp2/OneDrive - CDC/Cambodia_03_25_19/analysis/cambodia_g6pd/style.css
    includes:
      before_body: title.html
---


<div class="watermark">PRELIMINARY</div>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      fig.width = 7,
                      fig.height = 6,
                      dpi = 500,
                      warning = FALSE,
                      message = FALSE)

```


<!-- ======================================================= -->
<!-- ======================================================= -->
<!-- ======================================================= -->

# Basic Metrics {.tabset .tabset-fade .tabset-pills}

```{r}
pacman::p_load(linelist, 
               janitor, 
               Hmisc,
               ggdist,
               flextable,
               tidyverse)

pal <- c("#00447C", "#404756", "#A4ABBD", "#573F02", "#8D6E33")
```


```{r }
source("functions.R")
source("data_import_clean.R")

obs <- nrow(mccm_full) %>% 
  as.numeric()

n_house <- nrow(mccm_house)%>% 
  as.numeric()

n_indiv <- nrow(mccm_indiv) %>% 
  as.numeric()


#  individual database counts
unique_hf <- mccm_indiv %>% 
  distinct(district, hf) %>% 
  group_by(district) %>% 
  summarise(facilities = n())

u_hf <- unique_hf %>% 
  pull(2) %>% 
  as.numeric()


unique_catchment <- mccm_indiv %>% 
  distinct(district, hf, catchment) %>% 
  group_by(district, hf) %>% 
  summarise(villages = n())

min_village <- unique_catchment %>% 
  pull(2) %>% 
  as.numeric() %>% 
  min()

max_village <- unique_catchment %>% 
  pull(2) %>% 
  as.numeric() %>% 
  max()



latest <- format(max(mccm_house$sdi_interview_date), format = "%d %B %Y")
earliest <- format(min(mccm_house$sdi_interview_date), format = "%d %B %Y")



```

Data in this file were collected from `r earliest` to `r latest`. 
There are`r obs` observations;`r n_indiv` individuals from `r n_house` 
households. 

Data were obtained from `r u_hf` health facilities, with the number of villages
in each ranging from `r min_village` to `r max_village`.

# Participant review
```{r}
dup_house <- mccm_house %>% 
  get_dupes(sdi_householdid) %>% 
  nrow() %>% 
  as.numeric()

dup_indiv <- mccm_indiv %>% 
  get_dupes(unique_id) %>% 
  nrow() %>% 
  as.numeric()

dup_rdt <- mccm_indiv %>% 
  filter(!is.na(rdt_blood_id)) %>% 
  get_dupes(rdt_blood_id) %>% 
  nrow() %>% 
  as.numeric()


```

There are `r dup_house` duplicated household IDs, `r dup_indiv` duplicated 
individual study IDs, and `r dup_rdt` duplicated laboratory IDs on dried 
blood spots.

The following dried blood spot IDs should be verified. They are either 
internally inconsistent or have the inappropriate number of digits.

```{r}
rdt_id <- mccm_indiv %>% 
  filter(!is.na(rdt_blood_id)) %>% 
  mutate(id_ok = rdt_blood_id==rdt_blood_id_2) %>% 
  filter(id_ok == F | is.na(id_ok)) %>% 
  select(sdi_householdid, individual_id, sdi_interview_date, 
         rdt_blood_id, rdt_blood_id_2)


  
rdt_id2 <- mccm_indiv %>% 
  filter(!is.na(rdt_blood_id)) %>% 
  mutate(id_ok = str_length(rdt_blood_id)) %>% 
  filter(id_ok != 6)%>% 
  select(sdi_householdid, individual_id, sdi_interview_date, 
         rdt_blood_id, rdt_blood_id_2) %>% 
  bind_rows(rdt_id)


flextable(rdt_id2)

```


``` {r}

unique_household <- mccm_indiv %>% 
  distinct(district, hf, catchment, household) %>% 
  group_by(district, hf, catchment) %>% 
  summarise(households = n()) %>% 
  ungroup() %>% 
  mutate(perc = paste0(as.character(round(100*households/33, 0)), "%"))
  
  

ggplot(unique_household)+
  geom_hline(yintercept = 33, linetype = "dashed")+
  geom_col(aes(x=catchment, y = households), fill = pal[2])+
  geom_text(aes(catchment, y = households-1.5, label = perc),
    hjust = 0.45,
    nudge_y = 0.3,
    colour = "white",
    size = 4
  )+
  theme_minimal()+
  labs(x = "Village ID", 
       y = "Number of Households")+
  facet_grid(~district)
```

``` {r}
unique_indiv <- mccm_indiv %>% 
  group_by(district, hf, catchment) %>% 
  summarise(persons = n(), 
            ill = sum(hdi_b03_ill == 0, na.rm = T),
            rdt = sum(rdt_done == 0, na.rm = T)) %>% 
  pivot_longer(!c(district, catchment, hf), names_to = "type", 
               values_to = "counts") %>% 
  mutate(type = factor(type, levels = c("persons", 
                                        "ill", 
                                        "rdt")))

ggplot(unique_indiv)+
  geom_col(aes(x=catchment, y = counts, fill = type), position = "dodge2")+
  scale_fill_manual(values = pal[1:3], labels = c("Participants", "Recently Ill",
                                                  "RDT Done"))+
  theme_minimal()+
  theme(legend.title = element_blank())+
  labs(x = "Village ID", 
       y = "Number of Participants")+
  facet_grid(~district)


```

## Household size
Do not currently have access to enumeration lists to ensure consistency across 
tools.Here the number of individuals entered per house is compared with the 
response to the question explicitly asking how many individuals live in the home.

```{r}
house_num <- mccm_house %>% 
select(sdi_householdid, hdi_b02_wk)

indiv_num <- mccm_indiv %>% 
  group_by(sdi_householdid) %>% 
  summarise(num = n()) %>% 
  left_join(house_num, by = "sdi_householdid") %>% 
  filter(num != hdi_b02_wk) %>% 
  mutate(diff = abs(num - hdi_b02_wk)) %>% 
  rename(`Participants Entered` = num, 
         `Response to Question` = hdi_b02_wk)


```

The maximum observed difference between these values is `r max(indiv_num$diff)`
persons. Each household with a discrepancy is shown below. The reasons for each 
cannot be determined at the data cleaning phase, making changes to the response
potentially unreliable.

```{r}
indiv_num %>% 
  select(-diff) %>% 
  rename(`Household ID` = sdi_householdid) %>% 
  flextable()
```


```{r}
mccm_indiv %>% 
  group_by(sdi_householdid) %>% 
  summarise(num = n()) %>% 
ggplot(aes(x = num)) + 
  geom_bar()+
  theme_minimal()+
  labs(x = "Household Size", 
       y = "Count")
  
```

## Participant age distribution
```{r}
ggplot(mccm_indiv, aes(x = age_yr, y = 1)) + 
  ggdist::stat_halfeye(adjust = .5, 
    width = .25, 
    .width = 0, 
   # justification = -.3, 
    point_colour = NA) + 
  geom_boxplot(
    width = .1, 
   # outlier.shape = 3, 
    outlier.color = pal[5], 
   lwd = 1.5
  ) +
  theme_minimal()+
  labs(x = "Participant age (years)", 
       y = "")+
  theme(axis.text.y=element_blank(),
      axis.ticks.y=element_blank())
```

# Variable Examination
The following variables/questions, have no data associated with them. These are
likely skipped by the survey skip pattern (either appropriately or 
inappropriately).

```{r}

empty_vars <- mccm_full %>% 
  keep(~all(is.na(.)))

no_data <- names(empty_vars) %>% 
  as_tibble() %>% 
  left_join(questions, by = c("value" = "variable_name")) %>% 
  rename(`Variable Name` = value, 
         `Question` = description)

flextable(no_data)

```


```{r}
test <- mccm_indiv %>% 
  mutate(age_class = case_when(age_yr < 5 ~ "Under5", 
                               age_yr < 15 ~ "Five_14", 
                               age_yr <= 100 ~ "15+", 
                               TRUE ~ "Error"), 
         hdi_b03_ill = recode(hdi_b03_ill, `0` = "Yes", `1` = "No"),
         hmi_d01_fever = recode(hmi_d01_fever, `0` = "Yes", `1` = "No", 
                                `2` = "Don't Know"),
         hmi_d02_seek_treatment = recode(hmi_d02_seek_treatment, `0` = "Yes", 
                                         `1` = "No"), 
         hmi_d02_blood_taken = recode(hmi_d02_blood_taken, `0` = "Yes", `1` = "No", 
                                `2` = "Don't Know"), 
         hmi_d02_blood_result = recode(hmi_d02_blood_result, `1` = "Positive",
                                       `2` = "Negative", 
                                `3` = "Don't Know"),
         al = ifelse((md_antimalarial_1 == 1 | md_antimalarial_2 == 1 |
         md_antimalarial_3 == 1 | md_antimalarial_4 == 1), "Yes", 
         ifelse((md_antimalarial_17 == 1 | md_antimalarial_5 == 1 | 
         md_antimalarial_6 == 1 | md_antimalarial_7 == 1 | 
           md_antimalarial_8 == 1 | md_antimalarial_9 == 1 | 
           md_antimalarial_10 == 1 | md_antimalarial_11 == 1 | 
           md_antimalarial_12 == 1 | md_antimalarial_13 == 1 |
           md_antimalarial_14 == 1 | md_antimalarial_15 == 1 | 
           md_antimalarial_16 == 1 | md_antimalarial_99 == 1), "Other", "None"))) %>% 
  group_by(age_class, hdi_b03_ill, hmi_d01_fever, hmi_d02_seek_treatment,
  hmi_d02_blood_taken, hmi_d02_blood_result, al) %>% 
  summarise(num = n(), 
            ids = list(unique_id))


bad1 <- test %>% 
  filter(hdi_b03_ill == "No" & hmi_d01_fever == "Yes")

bad1a <- sum(bad1$num) %>% 
  as.numeric()

bad2 <- test %>% 
  filter(hmi_d01_fever == "No" & hmi_d02_seek_treatment == "Yes")

bad2a <- sum(bad2$num) %>% 
  as.numeric()
```

There are `r bad1a` individuals listed as not being ill, but having fever in the
past two weeks. Additionally, `r bad2a` individuals were not listed as having 
fever but noted seeking care for fever.

A table listing the number of individuals with all combinations of age group, 
presence of illness in the past two weeks, presence of fever in the past two
weeks, whether or not care was sought for fever, whether or no blood was taken 
for a test for malaria, malaria test results and if AL was taken by the 
individual is listed below.


```{r}
test %>% 
  select(-ids) %>% 
flextable()
```


```{r}

#install.packages("misty")
c <- Hmisc::describe(mccm_indiv)
a <- mccm_indiv %>% 
  select(contains("other")) %>% 
  names()

b <- mccm_indiv %>% 
  select(-all_of(a))

test <- misty::na.pattern(b)
misty::na.test(b)

test1 <- test[["result"]] %>% 
  arrange(desc(n)) %>% 
  select(-pattern) %>% 
  slice(-1) %>% 
  mutate(id = row_number())

```

